Analytics without Tuning Considered Harmful?\\(Two Case Studies in Defect Prediction)

### 2015-03-02 tuningpredictor.tex
add experimental results

\documentclass{sig-alternative}
\usepackage{multirow}
\usepackage{color}
\usepackage{colortbl}
\usepackage{picture}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\newcommand{\quart}[3]{\begin{picture}(100,6)%1
{\color{black}\put(#3,3){\circle*{4}}\put(#1,3){\line(1,0){#2}}}\end{picture}}

@@

\conferenceinfo{FSE}{'15 Bergamo, Italy}
\title{Analytics without Tuning Considered Harmful?\\(Two Case Studies in Defect Prediction)}
\numberofauthors{1}
\author{
\alignauthor
Wei Fung, Tim Menzies\\
       \affaddr{Computer Science, North Carolina State University, USA}\\
       {wfu@ncsu.edu, tim.menzies@gmail.com}}

@@

\vspace{1mm}
\noindent
{\bf General Terms:} Experimentation, Algorithm}

@@

% Given N instances, instead of building decision tree directly with CART, we use WHERE to 
%cluster instances. 
WHERE is a fast clustering algorithm designed by {\it menzies} for finding software artifacts 
with similar attributes. It clusters data on dimensions synthesized along the axis of greatest 
variability in the data. The way WHERE used to find such dimension is a linear-time heuristic 
called ``FASTMAP" proposed by Faloutsos \& Lin\cite{faloutsos1995fastmap}. ``FASTMAP" 
randomly picks one instance Z; find the instance {\it east} X that's furthest away form Z; find 
the instance {\it west} Y that's furthest away from {\it east} X. Next, project all the remaining 
points onto the line drawn between X and Y. Then choose the median point as the split and 
recursively divide all the instances into {\it west} and {\it east} clusters until the number of 
instances within each cluster is less than specific minimum size. The representation of the 
clustering result is a tree, we call it Where-clustering tree. Such tree will be pruned if applicable 
in some cases. Finally, cluster labels  will be assigned to instances in each of those 
clusters(leaves).

Then based on the attributes and the cluster labels in each instances,  we build a 
decision tree based on CART algorithm. In each leaf of the tree, there're several instances 
falling in. This will be the model trained for defect prediction. During testing process, a new 
instance comes in and traverses the tree according to 
values of the its attributes. If the instance could reach one leaf of the tree, the predicted value 
of this instance will be the mean  of all the training data values associated with this leaf. 
Otherwise if stops at intermediate nodes of tree, the predicted value will be the mean of the all 
the training data value below this node. After estimating all the number of defectives in the test 
data, whether each instance contains defectives will be determined by comparing with a threshold value. If the predicted value is greater than threshold, the Where-based learner will predict this instance as defective otherwise non-defective.

@@

\begin{figure*}[t!]
\scriptsize
  \centering
	\begin{tabular}{|c|c|c|c|l|}
	\hline
	\begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular} & Parameters & Default &\begin{tabular}[c]{@{}c@{}}Tuning\\ Range\end{tabular}& 
\multicolumn{1}{c|}{Description} \\ \hline
	\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where-based\\ Learner\end{tabular}} 
	& threshold & 0.5 &[0,1]& The value to determine defective or not .\\ \cline{2-5} 
	& infogain & 0.33 &[0,1]& The percentage of features to consider  for the best 
split to build CART tree\footnote{Since the Where-based learner will build two trees, the first 
one is for clustering and the second one is building prediction model. we explicitly call Where-
clustering tree and CART tree, respectively}. \\ \cline{2-5} 
	 & min\_sample\_size & 4& [1,10]& The minimum number of samples required to be a leaf for 
CART tree. \\ \cline{2-5} 
	 & min\_Size & 0.5 &[0,1]& \begin{tabular}[c]{@{}l@{}}The value to determine the minimum 
number of samples to be a Where-clustering tree \\ based on  ${n\_samples}^ {min\_Size}$.
\end{tabular} \\ \cline{2-5} 
	 & depthMin & 2 & [1,6]&The minimum depth of the tree below which no pruning for Where-
clustering tree. \\ \cline{2-5} 
	 & depthMax & 10 &[1,20]& The maximum depth of the Where-clustering tree. \\ \cline{2-5} 
	 & wherePrune & False &T/F& Whether or not to prune the Where-clustering tree. \\ \cline{2-5} 
	 & treePrune & True &T/F& Whether or not to prune the classification tree built by CART. \\ 
\hline
	\multirow{5}{*}{CART} & threshold & 0.5 &[0,1]& The value to determine defective or not. \\ 
\cline{2-5} 
	 & max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
split. \\ \cline{2-5} 
	 & max\_depth & None &[1,50]& The maximum depth of the tree. \\ \cline{2-5} 
	 & min\_sample\_split & 2 &[2,20]& The minimum number of samples required to split an 
internal node. \\ \cline{2-5} 
	 & min\_smaples\_leaf & 1 & [1,20]&The minimum number of samples required to be at a leaf 
node. \\ \hline  
       \multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}}  & threshold & 0.5 & - & The value to determine defective or not. \\ 
\cline{2-5} 
	 & max\_feature & None &-& The number of features to consider when looking for the best 
split. \\ \cline{2-5} 
	 & max\_depth & None &-& The maximum depth of the tree. \\ \cline{2-5} 
	 & min\_sample\_split & 2 &-& The minimum number of samples required to split an 
internal node. \\ \cline{2-5} 
	 & min\_smaples\_leaf & 1 & -&The minimum number of samples required to be at a leaf 
node. \\ \cline{2-5} 
	 &  n\_estimators & 100 & -&The number of trees in the forest.\\ \hline

\section{Result}
\begin{figure}[!th]

{\scriptsize
{\scriptsize \begin{tabular}{l@{~~~}l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
\arrayrulecolor{darkgray}
\rowcolor[gray]{0.75} Dataset     & Methods  & median &IQR&  \\ 
\rowcolor[gray]{.9}ant & Naive\_WHERE & 0 & 0 & \quart{0.0}{0}{0.0}\\
 & Naive\_Cart & 51 & 2 & \quart{51.0}{2}{52.0}\\
 & Naive\_RFst & 53 & 1 & \quart{52.0}{1}{53.0}\\
 & Tuned\_Cart & 63 & 0 & \quart{63.0}{0}{63.0}\\
 & Tuned\_WHERE & 72 & 0 & \quart{72.0}{0}{72.0}\\
\rowcolor[gray]{.9}camel & Naive\_WHERE & 45 & 0 & \quart{45.0}{0}{45.0}\\
 & Naive\_Cart & 54 & 2 & \quart{54.0}{2}{54.0}\\
 & Tuned\_WHERE & 56 & 0 & \quart{56.0}{0}{56.0}\\
 & Tuned\_Cart & 56 & 2 & \quart{56.0}{2}{57.0}\\
 & Naive\_RFst & 56 & 1 & \quart{57.0}{1}{57.0}\\
\rowcolor[gray]{.9}ivy & Naive\_RFst & 50 & 1 & \quart{50.0}{1}{50.0}\\
 & Naive\_WHERE & 54 & 0 & \quart{54.0}{0}{54.0}\\
 & Naive\_Cart & 57 & 1 & \quart{58.0}{1}{58.0}\\
 & Tuned\_Cart & 68 & 0 & \quart{68.0}{0}{68.0}\\
 & Tuned\_WHERE & 70 & 0 & \quart{70.0}{0}{70.0}\\
\rowcolor[gray]{.9} jedit & Naive\_WHERE & 49 & 0 & \quart{49.0}{0}{49.0}\\
 & Naive\_Cart & 55 & 15 & \quart{55.0}{15}{55.0}\\
 & Tuned\_WHERE & 62 & 0 & \quart{62.0}{0}{62.0}\\
 & Tuned\_Cart & 65 & 3 & \quart{65.0}{3}{66.0}\\
 & Naive\_RFst & 74 & 2 & \quart{73.0}{2}{74.0}\\
 \rowcolor[gray]{.9} log4j & Naive\_Cart & 48 & 1 & \quart{47.0}{1}{48.0}\\
 & Tuned\_WHERE & 50 & 0 & \quart{50.0}{0}{50.0}\\
 & Naive\_WHERE & 53 & 0 & \quart{53.0}{0}{53.0}\\
 & Tuned\_Cart & 55 & 4 & \quart{55.0}{4}{57.0}\\
 & Naive\_RFst & 56 & 0 & \quart{57.0}{0}{57.0}\\
\rowcolor[gray]{.9}lucene & Naive\_WHERE & 37 & 0 & \quart{37.0}{0}{37.0}\\
 & Naive\_RFst & 56 & 1 & \quart{56.0}{1}{56.0}\\
 & Naive\_Cart & 57 & 1 & \quart{57.0}{1}{58.0}\\
 & Tuned\_Cart & 57 & 4 & \quart{57.0}{4}{58.0}\\
 & Tuned\_WHERE & 61 & 0 & \quart{61.0}{0}{61.0}\\
\rowcolor[gray]{.9}synapse & Naive\_WHERE & 0 & 0 & \quart{0.0}{0}{0.0}\\
 & Naive\_Cart & 42 & 2 & \quart{41.0}{2}{42.0}\\
 & Naive\_RFst & 43 & 4 & \quart{43.0}{4}{44.0}\\
 & Tuned\_Cart & 49 & 11 & \quart{49.0}{11}{49.0}\\
 & Tuned\_WHERE & 64 & 0 & \quart{64.0}{0}{64.0}\\
\rowcolor[gray]{.9}velocity & Naive\_WHERE & 1 & 0 & \quart{1.0}{0}{1.0}\\
 & Naive\_RFst & 9 & 0 & \quart{9.0}{0}{9.0}\\
 & Naive\_Cart & 27 & 2 & \quart{26.0}{2}{27.0}\\
 & Tuned\_Cart & 49 & 5 & \quart{46.0}{5}{50.0}\\
 & Tuned\_WHERE & 57 & 0 & \quart{58.0}{0}{58.0}\\
\rowcolor[gray]{.9}xalan & Tuned\_Cart & 51 & 4 & \quart{49.0}{4}{51.0}\\
 & Tuned\_WHERE & 56 & 0 & \quart{57.0}{0}{57.0}\\
 & Naive\_Cart & 66 & 0 & \quart{66.0}{0}{66.0}\\
 & Naive\_WHERE & 69 & 0 & \quart{69.0}{0}{69.0}\\
 & Naive\_RFst & 73 & 1 & \quart{73.0}{1}{73.0}\\
\rowcolor[gray]{.9}xerces & Naive\_RFst & 18 & 1 & \quart{18.0}{1}{18.0}\\
 & Naive\_Cart & 19 & 1 & \quart{18.0}{1}{19.0}\\
 & Tuned\_Cart & 25 & 7 & \quart{24.0}{7}{26.0}\\
 & Naive\_WHERE & 26 & 0 & \quart{26.0}{0}{26.0}\\
 & Tuned\_WHERE & 34 & 1 & \quart{34.0}{1}{34.0}\\

 \end{tabular}}

}

\caption{Results over Different Data Sets}\label{fig:g feature}
\end{figure}

@@

\section*{Acknowledgements}
This work was partially funded by an National Science
Foundation grant NSF-CISE 1302169.

\vspace*{0.5mm}
\scriptsize

\bibliographystyle{unsrt}
\bibliography{tuningpredictor}  
\end{document}

>>>>

\documentclass{sig-alternative}
\usepackage{multirow}
\usepackage{color}
\usepackage{graphics}
\usepackage{rotating}
\usepackage{graphics}
\usepackage{colortbl}
\usepackage{picture}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\definecolor{lightgray}{gray}{0.8}
\definecolor{darkgray}{gray}{0.6}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
%%% graph
\newcommand{\crule}[3][darkgray]{\textcolor{#1}{\rule{#2}{#3}}}
\newcommand{\rone}{\crule{1mm}{1.95mm}}
\newcommand{\rtwo}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}}
\newcommand{\rthree}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}}
\newcommand{\rfour}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}} 
\newcommand{\rfive}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}}
\newcommand{\quart}[3]{\begin{picture}(100,6)%1
{\color{black}\put(#3,3){\circle*{4}}\put(#1,3){\line(1,0){#2}}}\end{picture}}
\definecolor{Gray}{gray}{0.95}
\definecolor{LightGray}{gray}{0.975}

@@

\conferenceinfo{FSE}{'15 Bergamo, Italy}
\title{Analytics without Tuning Considered Harmful?\\(Two Case Studies in Defect Prediction)}
\numberofauthors{1}
\author{
\alignauthor
Wei Fu, Tim Menzies\\
       \affaddr{Computer Science, North Carolina State University, USA}\\
       {wfu@ncsu.edu, tim.menzies@gmail.com}}

@@

\vspace{1mm}
\noindent
{\bf General Terms:} Experimentation, Algorithm

@@

% Given N instances, instead of building decision tree directly with CART, we use WHERE to 
%cluster instances. 
WHERE is a fast clustering algorithm designed by {\it menzies} for finding software artifacts 
with similar attributes. It clusters data on dimensions synthesized along the axis of greatest 
variability in the data. The way WHERE used to find such dimension is a linear-time heuristic 
called ``FASTMAP" proposed by Faloutsos \& Lin\cite{faloutsos1995fastmap}. ``FASTMAP" 
randomly picks one instance $Z$; find the instance {\it east} $X$ that's furthest away form $Z$; find 
the instance {\it west} $Y$ that's furthest away from {\it east} $X$. Next, project all the remaining 
points onto the line drawn between $X$ and $Y$.  The line $\overline{XY}$ is an approximation of the 
first component found by PCA. As shown in Figure \ref{Where}, $X$ and $Y$ are the furthest points found by ``FASTMAP'' and $\overline{XY}$ is of length $c$. Each point in this figure has a distance $a$
to $X$ and distance $b$ to $Y$. According to the coisne rule and Pythagoras, each instance will be mapped 
into 2-dimension by the following equations.
\begin{equation}
	\begin{split}
			x  &= (a^2 +c^2-b^2)/(2c)\\ 
		    y  &= \sqrt{a^2 -x^2}
	\end{split}
\end{equation}

Then choose the median point $\hat{x}$ as the split and 
recursively divide all the instances into {\it west} and {\it east} clusters until the number of 
instances within each cluster is less than specific minimum size. The representation of the 
clustering result is a tree, we call it Where-clustering tree. Such tree will be pruned if applicable 
in some cases. Finally, cluster labels  will be assigned to instances in each of those 
clusters(leaves).

\begin{figure}[!ht]
\includegraphics[scale=0.5]{where.png}
\caption{WHERE algoirthm }
\label{Where}
\end{figure}
Then based on the attributes and the cluster labels in each instances,  we build a 
decision tree based on CART algorithm. In each leaf of the tree, there're several instances 
falling in. This will be the model trained for defect prediction. During testing process, a new 
instance comes in and traverses the tree according to 
values of the its attributes. If the instance could reach one leaf of the tree, the predicted value 
of this instance will be the mean  of all the training data values associated with this leaf. 
Otherwise if stops at intermediate nodes of tree, the predicted value will be the mean of the all 
the training data value below this node. After estimating all the number of defectives in the test 
data, whether each instance contains defectives will be determined by comparing with a threshold value. If the predicted value is greater than threshold, the Where-based learner will predict this instance as defective otherwise non-defective.

@@

\section{Result}

@@

\section{Acknowledgments}

\bibliographystyle{unsrt}
\bibliography{tuningpredictor}

%%%%%%%%%%%%%%%% list of parameters%%%%%%%%%%%%%%%%%%%%%
\renewcommand\arraystretch{1.2}
\begin{figure*}[t!]
\scriptsize
  \centering
	\begin{tabular}{|c|c|c|c|l|}
	\cline{1-5}
	\begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular} & Parameters & Default &\begin{tabular}[c]{@{}c@{}}Tuning\\ Range\end{tabular}& 
\multicolumn{1}{c|}{Description} \\ \hline
	\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where-based\\ Learner\end{tabular}} 
	& threshold & 0.5 &[0.01,1]& The value to determine defective or not .\\ \cline{2-5} 
	& infogain & 0.33 &[0.01,1]& The percentage of features to consider  for the best 
split to build CART tree\footnote{Since the Where-based learner will build two trees, the first 
one is for clustering and the second one is building prediction model. we explicitly call Where-
clustering tree and CART tree, respectively}. \\ \cline{2-5} 
	 & min\_sample\_size & 4& [1,10]& The minimum number of samples required to be a leaf for 
CART tree. \\ \cline{2-5} 
	 & min\_Size & 0.5 &[0.01,1]& \begin{tabular}[c]{@{}l@{}}The value to determine the minimum 
number of samples to be a Where-clustering tree \\ based on  ${n\_samples}^ {min\_Size}$.
\end{tabular} \\ \cline{2-5} 
    & wriggle & 0.2 &[0.01, 1] & The threshold to determine which branch in  Where tree to be pruned\\ \cline{2-5}
	 & depthMin & 2 & [1,6]&The minimum depth of the tree below which no pruning for Where-
clustering tree. \\ \cline{2-5} 
	 & depthMax & 10 &[1,20]& The maximum depth of the Where-clustering tree. \\ \cline{2-5} 
	 & wherePrune & False &T/F& Whether or not to prune the Where-clustering tree. \\ \cline{2-5}
	 & treePrune & True &T/F& Whether or not to prune the classification tree built by CART. \\ \cline{2-5} 
\hline
\multirow{4}{*}{CART} & threshold & 0.5 &[0,1]& The value to determine defective or not. \\ \cline{2-5} 
	 & max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
split. \\ \cline{2-5}

	 & min\_sample\_split & 2 &[2,20]& The minimum number of samples required to split an 
internal node. \\ \cline{2-5} 
	 & min\_smaples\_leaf & 1 & [1,20]&The minimum number of samples required to be at a leaf 
node. \\ \cline{1-5}  
       \multirow{5}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}}  & threshold & 0.5 & [0.01,1] & The value to determine defective or not. \\ 
\cline{2-5} 
	 & max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
split. \\ \cline{2-5} 
	 & max\_leaf\_nodes & None &[1,50]& Grow trees with max\_leaf\_nodes in best-first fashion. \\ \cline{2-5} 
	 & min\_sample\_split & 2 &[2,20]& The minimum number of samples required to split an 
internal node. \\ \cline{2-5} 
	 & min\_smaples\_leaf & 1 &[1,20]&The minimum number of samples required to be at a leaf 
node. \\ \cline{2-5} 
	 &  n\_estimators & 100 & [50,150]&The number of trees in the forest.\\ \cline{2-5}
	 \hline

%%%%%%%%%%%%%%%% optimal parameters from tuning process%%%%%%%%%%%%%%%%%%%%%
%\begin{figure*}[t!]
%\scriptsize
%  \centering
%	\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
%	\hline
%	\begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default & 
%ant  & camel &ivy & jedit & log4j & lucene & poi & synapse & velocity & xalan & xerces \\ \hline
%	\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where-based\\ Learner\end{tabular}} 
%	& threshold & 0.5 & 0.16 & 0.87 &0.89 & 0.68 &0.58 &0.62&0.06&0.09&1&0.64 &0.02\\ \cline{2-14} 
%	& infogain & 0.33 & 0.33 & 0.49 &1&0.82 &0.12 &0.54&0.38&0.01&1&0.36&0.25\\ \cline{2-14} 
%	 & min\_sample\_size & 4& 8 &1 &1&5&8&1&5&9&1&5&5\\ \cline{2-14} 
%	 & min\_Size & 0.5& 1 & 0.67 & 0.99&1&0.63&1&0.95&0.59&1&0.88 &0.64\\ \cline{2-14} 
%	 & wriggle &
%	 & depthMin & 2 & 3 & 4 &1&1&2&1&1&5&1&1&3\\ \cline{2-14} 
%	 & depthMax & 10 & 8 &14 &16&18&1&16&13&5&9&18&20\\ \cline{2-14} 
%	 & wherePrune & False & True & True &False&False&False&True&True&False&True&False &True\\ \cline{2-14} 
%	 & treePrune & True& False & True &True&True&False&False&True&False&False&False &False\\ 
%\hline
%	\multirow{4}{*}{CART} 
%	& threshold & 0.5 & 0.01 & 0.98 &0.94&0.67&0.47&1&0.01&0.12&0.9&0.57 &0.01\\ \cline{2-14} 
%	 & max\_feature & None &0.01 & 1 &0.29&0.28&0.53&0.13&0.01&0.01&0.87&0.47 &0.01\\ \cline{2-14} 
%	 %& max\_depth & None &27 & 46 &33&21&42&36&39&17&29&11&31\\ \cline{2-14} 
%	 & min\_sample\_split & 2 &6 &2 &13&17&12&2&14&12&7&16 &13\\ \cline{2-14} 
%	 & min\_smaples\_leaf & 1 &6 &3 &18&12&3&10&4&20&8&11&1\\ \hline  
%    \multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}}  
%    & threshold & 0.5 & 0.06 &0.88 &1&0.73&0.41&0.81&0.11&0.16&1&0.63&0.29\\ \cline{2-14} 
%	 & max\_feature & None & 0.21 &0.98 &0.78&0.73&0.36&0.35&0.01&0.01&0.01&0.65 &0.89\\ \cline{2-14} 
%	 & max\_leaf\_nodes & None & 31 &35 &41&40&23&12&26&41&46&49&35\\ \cline{2-14} 
%	 & min\_sample\_split & 2 &12 &14 &2&5&8&11&1&16&1&9&20\\ \cline{2-14} 
%	 & min\_smaples\_leaf & 1 &6 &15 &2&17&3&9&19&8&2&14&9\\ \cline{2-14} 
%	 &  n\_estimators & 100 &111 &120 &89&68&64&84&107&100&79&113&50\\ \hline
%
%	\end{tabular}
%    \caption {Optimal parameters from tuning process with objetive of G measure over different data sets.}
%\label{fig:parameters}
%\end{figure*}

%%%%parameters for pd %%%%%%
\begin{figure*}[!ht]
\resizebox{\textwidth}{!}{
\scriptsize
\centering
  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
    \hline
  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\ 
 \hline
\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
& threshold& 0.5& 0.17& 0.17& 0.02& 0.04& 0.42& 0.7& 0.8& 0.25& 0.32& 0.13& 0.61& 0.77& 0.09& 0.02& 0.68& 0.17& 0.01\\ \cline{2-20}
& infoPrune& 0.33& 0.13& 0.06& 0.12& 0.35& 0.44& 0.26& 0.33& 0.81& 0.03& 0.32& 0.89& 0.05& 0.1& 0.97& 0.15& 0.24& 0.01\\ \cline{2-20}
& min\_sample\_size& 4& 5& 2& 4& 1& 7& 6& 9& 6& 9& 8& 1& 3& 3& 9& 5& 4& 2\\ \cline{2-20}
& min\_Size& 0.5& 0.49& 0.24& 0.41& 0.26& 0.12& 0.03& 0.26& 0.06& 0.19& 0.38& 0.02& 0.07& 0.2& 0.2& 0.32& 0.13& 0.86\\ \cline{2-20}
& wriggle& 0.2& 0.65& 0.19& 0.42& 0.37& 0.22& 0.56& 0.64& 0.26& 0.79& 0.97& 0.23& 0.52& 0.99& 0.78& 0.15& 0.58& 0.55\\ \cline{2-20}
& depthMin& 2& 4& 3& 2& 5& 5& 4& 3& 5& 4& 4& 2& 4& 2& 1& 4& 3& 1\\ \cline{2-20}
& depthMax& 10& 16& 7& 19& 11& 14& 16& 12& 12& 19& 17& 12& 13& 15& 13& 3& 17& 15\\ \cline{2-20}
& wherePrune& False& True& False& False& False& False& False& False& True& True& False& False& True& False& True& False& False& False\\ \cline{2-20}
& treePrune& True& True& True& True& False& False& False& False& False& True& True& False& False& True& False& False& True& False\\ \cline{2-20}
\hline
\multirow{4}{*}{CART}
& threshold& 0.5& 0.01& 0.13& 0.01& 0.01& 0.06& 0.34& 0.01& 0.15& 0.39& 0.01& 0.05& 0.06& 0.01& 0.01& 0.18& 0.06& 0.01\\ \cline{2-20}
& max\_feature& None& 0.01& 0.9& 0.01& 0.01& 0.45& 0.14& 0.52& 0.57& 0.76& 1& 0.68& 0.01& 0.33& 0.01& 0.73& 0.04& 0.01\\ \cline{2-20}
& min\_samples\_split& 2& 17& 20& 7& 18& 9& 11& 15& 16& 12& 11& 2& 6& 3& 13& 19& 13& 10\\ \cline{2-20}
& min\_samples\_leaf& 1& 11& 1& 9& 2& 19& 14& 6& 15& 4& 17& 19& 9& 12& 5& 4& 7& 13\\ \cline{2-20}
\hline
\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
& threshold& 0.5& 0.09& 0.01& 0.01& 0.01& 0.36& 0.49& 0.08& 0.01& 0.01& 0.01& 0.05& 0.01& 0.01& 0.01& 0.2& 0.15& 0.01\\ \cline{2-20}
& max\_feature& None& 0.01& 0.63& 0.01& 1& 0.19& 0.17& 0.01& 0.01& 0.95& 0.01& 0.65& 0.54& 0.01& 0.01& 0.45& 0.63& 0.2\\ \cline{2-20}
& max\_leaf\_nodes& None& 31& 43& 28& 29& 11& 48& 17& 25& 13& 25& 10& 31& 33& 47& 44& 14& 23\\ \cline{2-20}
& min\_samples\_split& 2& 2& 7& 13& 1& 9& 13& 1& 13& 6& 10& 4& 12& 19& 16& 17& 3& 13\\ \cline{2-20}
& min\_samples\_leaf& 1& 17& 18& 2& 20& 2& 18& 9& 6& 7& 11& 17& 19& 8& 17& 3& 13& 9\\ \cline{2-20}
& n\_estimators& 100& 76& 64& 62& 141& 91& 67& 57& 104& 70& 67& 56& 59& 97& 81& 140& 85& 92\\ \cline{2-20}
\hline  \end{tabular}
}
  \caption{Parameters tuned on different models over the objective of pd}
\end{figure*}

%%%%parameters for pf %%%%%%
\begin{figure*}[!ht]
\resizebox{\textwidth}{!}{
\scriptsize
\centering
  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
    \hline
  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\ 
 \hline
\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
& threshold& 0.5& 0.53& 0.71& 0.37& 0.23& 0.67& 1& 1& 0.48& 0.97& 0.81& 1& 0.98& 0.92& 0.93& 0.98& 0.5& 0.99\\ \cline{2-20}
& infoPrune& 0.33& 0.68& 0.97& 0.43& 0.01& 0.22& 1& 0.76& 0.48& 0.61& 0.23& 0.04& 0.92& 0.59& 0.41& 0.88& 0.9& 0.23\\ \cline{2-20}
& min\_sample\_size& 4& 3& 1& 2& 1& 6& 4& 3& 5& 3& 9& 7& 3& 3& 8& 7& 2& 9\\ \cline{2-20}
& min\_Size& 0.5& 0.07& 0.03& 0.36& 0.06& 0.21& 0.38& 0.15& 0.19& 0.29& 0.08& 0.35& 0.24& 0.38& 0.67& 0.01& 0.25& 0.58\\ \cline{2-20}
& wriggle& 0.2& 0.91& 0.97& 0.47& 0.96& 0.82& 0.11& 0.37& 0.37& 0.06& 0.68& 0.23& 0.01& 0.51& 0.79& 0.53& 0.05& 0.08\\ \cline{2-20}
& depthMin& 2& 4& 1& 3& 3& 1& 1& 3& 4& 2& 3& 3& 1& 1& 1& 1& 3& 1\\ \cline{2-20}
& depthMax& 10& 10& 15& 7& 4& 14& 3& 15& 16& 15& 18& 6& 6& 5& 18& 10& 6& 16\\ \cline{2-20}
& wherePrune& False& True& True& False& True& True& True& True& True& True& False& True& True& True& True& True& True& False\\ \cline{2-20}
& treePrune& True& True& False& True& False& False& True& True& False& False& False& False& True& False& False& False& True& False\\ \cline{2-20}
\hline
\multirow{4}{*}{CART}
& threshold& 0.5& 1& 1& 0.96& 0.88& 1& 1& 0.99& 0.88& 1& 0.83& 1& 1& 0.92& 0.9& 1& 1& 1\\ \cline{2-20}
& max\_feature& None& 0.01& 1& 0.93& 0.58& 0.01& 0.73& 1& 0.44& 0.01& 0.88& 0.01& 0.38& 0.48& 0.65& 0.86& 0.28& 0.01\\ \cline{2-20}
& min\_samples\_split& 2& 4& 4& 18& 3& 14& 19& 14& 16& 19& 12& 6& 2& 9& 8& 3& 6& 16\\ \cline{2-20}
& min\_samples\_leaf& 1& 12& 16& 19& 18& 1& 2& 5& 8& 8& 1& 10& 6& 12& 12& 13& 3& 10\\ \cline{2-20}
\hline
\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
& threshold& 0.5& 0.89& 0.58& 0.88& 0.86& 1& 1& 1& 1& 1& 1& 1& 1& 0.78& 0.73& 1& 1& 0.93\\ \cline{2-20}
& max\_feature& None& 0.47& 0.04& 0.12& 0.38& 0.96& 0.87& 0.11& 0.01& 1& 0.16& 0.85& 0.99& 0.78& 0.77& 0.01& 0.35& 0.23\\ \cline{2-20}
& max\_leaf\_nodes& None& 35& 37& 38& 23& 13& 34& 36& 29& 10& 10& 10& 10& 33& 49& 50& 24& 37\\ \cline{2-20}
& min\_samples\_split& 2& 18& 10& 5& 16& 1& 20& 2& 1& 10& 5& 11& 5& 16& 4& 5& 19& 19\\ \cline{2-20}
& min\_samples\_leaf& 1& 16& 11& 6& 13& 2& 4& 2& 2& 2& 19& 6& 2& 4& 14& 2& 3& 18\\ \cline{2-20}
& n\_estimators& 100& 103& 95& 76& 88& 68& 88& 136& 90& 144& 115& 150& 99& 110& 114& 53& 108& 99\\ \cline{2-20}
\hline  \end{tabular}
}
  \caption{Parameters tuned on different models over the objective of pf}
\end{figure*}
